Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits

### 2016-01-25 ms.tex
continued work

\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{etoolbox}

@@

Blah blah intro stuff...

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}
  \label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution. Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$, are used. When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. We prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements. \editorial{Maybe run a quick check to see how they compare.}

@@

The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators.

@@

Figure~\ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed versus the number of actual galaxies, as a function of both redshift and cluster mass for the targeted and survey observing strategies. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significant better than the survey observing strategy for nearly all redshifts and cluster masses. This performance gain is due solely to the gaps between the fiber bundles of the IFU.

@@

>>>>

\documentclass[fleqn,usenatbib]{mnras}

@@

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
%\usepackage{multirow}
%\usepackage{etoolbox}

@@

\editorial{Blah blah intro stuff... Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}
  \label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain sampler (MCMC; {\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution. Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$ \editorial{check}, are used. When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.

@@

The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators. \editorial{should talk about how random forests can give error bars on the individual estimates.}

@@

Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies, as function of both redshift and cluster mass. It is important to note that if few than five member galaxies are observed the cluster is not considered detected, and is excluded from this plot. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significant better than the survey observing strategy for nearly all redshifts and cluster masses.

\editorial{There is no obvious trend between number of galaxies observed and redshift. There is a trend between number of galaxies observed and cluster mass though. This is the "richness" and it's something that we should have expected. To test where the galaxies go we are going to apply an absolute magnitude cut instead of the apparent magnitude cut and then derive the catalog. That will let us know if things are going on.}

This performance gain is due solely to the gaps between the fiber bundles of the IFU.

@@

Any scatter in recovered masses can be attributed to both physical and numerical effects. As the cluster mass increases, clusters become more virialized and contain many individual galaxies. The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which can increase the observed LOSVD increasing the predicted mass. Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects. The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership. In reality, the mass recovery levels presented in this section represent a lower bound on the accuracy achievable through this method. \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaiminated galaxy catalogs. We could do something similar and have a similar discussion, but I'm not sure it is worth it. Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.}
